Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
edited first paragraph under thm 7.4

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$. This is the classical
case which is done, with $L$ replaced by $K$, \todo{Peter: I don't think its helpful to say with $L$ replaced by $K$.  It might slightly confuse the reader into thinking that replacing half canonical divisor with canonical divisor changes the problem.} by Voight and
Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.

>>>>

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$.  When $n=-1$, then $R_\halfcan=k$.  When $n=0$, then $R_\halfcan = k[x]$.  When $n>0$, inductively applying Lemma \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1 with relations generated in degree 2.  All three of these cases meet the conclusion of Theorem \ref{thm:g-0-main}.
